Test Title

### 2019-09-01 paper.tex
Start the preliminaries section

\documentclass{article}
\usepackage{authblk}

@@

This is a placeholder. Lorem ipsum. Lorem ipsum. Lorem ipsum...
Below is some intro of it copied from my SoP

@@

\section{more stuff}

>>>>

\documentclass{article}
\usepackage{authblk}
\usepackage{amsmath, amssymb, amsthm}

\newtheorem{theorem}{Theorem}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

@@

Below is some intro of it copied from my SoP.
This is unpolished and mostly a placeholder at the moment though.

@@

\subsection{Notations}

Let $H\in\mathbb{R}^{N\times N}$ be Hermitian.

\begin{definition}
	Let $\lambda(H)$ as the least eigenvalue of $H$.
\end{definition}

\begin{definition}
	Let the \emph{ground state} of $H$ be the eigenvector corresponding to $\lambda(H)$.
\end{definition}

\subsection{Local Hamiltonian}

The local Hamiltonian problem is defined as follows:

Given $H_1, \ldots, H_n\in\mathbb{R}^{N\times N}$, where each $H_j$ is Hermitian and has nonzero entries on at most $c\in\mathbb{N}$ rows and columns.
Given $a<b$ with some inverse polynomial gap, let $H=\sum H_j$, decide whether $\lambda(H)<a$ or $\lambda(H)>b$..

\begin{theorem}
	Local Hamiltonian is QMA-complete.
\end{theorem}

\section{The Scheme}

Here we describe the scheme between the classical client and an honest quantum server.

First, we apply the transform given in \cite{1109.0795} to the desired quantum circuit. Everything is real numbers from here on. Note that this preserves the results of X/Z measurements. Then, we transform the circuit following the projection lemma construction described in \cite{quant-ph/0406180}. Additionally, we also double the size of the circuit by padding identity matrices at the end. We then follow the rest of \cite{quant-ph/0406180} and reduce the circuit into a 2-Local Hamiltonian instance. We can then turn all the Hamiltonians involved into some combinations of $X$ and $Z$ matrices following \cite{0704.1287}.

We then follow \cite{1804.01082}. That is, the server would commit copies of the ground state of the Hamiltonian for the classical client to measure. The client would check whether the computation is done correctly using a modified Hamiltonian from \cite{quant-ph/0406180}. It will drop the $H_{out}$ term and simply set $H=J_{in}H_{in}+J_2H_{prop2}+J_1H_{prop1}+J_{clock}H_{clock}$.

\section{Stuff}
